\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2019-07-10 sections/introduction.tex
Change: Remove todo
Update intro (Daniel's corrections)

  Studies have shown the importance of specific microbial interactions in the healthy human microbiome \cite{Lloyd-Price2016} and others have shown how changes in these interactions can lead to dysbiosis \cite{Wang2017,Gilbert2016,Belizario2015}.
  Co-occurrence relationships in microbial communities are be driven by microbial interactions.
  Each interaction within this complex ecological network can have a positive effect, a negative effect or no effect on the species involved.
  Bacteria that compete for the same nutrient will have a negative co-occurrence relationship \cite{Ghoul2016} whereas cross-feeding between species leads to a positive co-occurrence relationship \cite{DSouza2018}.
  The microbial interaction networks are highly dynamic, and they constantly reorganize in a varying environment.
  Even under static conditions, these interactions are often difficult to predict due to their non-linear nature \cite{Konopka2015}.
  Compounding on this complexity is the fact that these interaction networks usually involve thousands of species.

@@

  The methodology for the analysis of 16S rRNA sequence data is not very straightforward and there are a myriad of tools for each step of the process, making the analysis complicated and not very reproducible.
  But because there does not exist a dataset wherein the microbial interactions have been fully characterized, there is no straightforward way to determine which set of tools or methods generate the most accurate networks.
  In this study, we propose to build a standardized 16S data-analysis pipeline that will produce robust and reproducible co-occurrence networks from community 16S sequence data. \todo[size=\footnotesize]{Mention DB?}
  We do this by conducting a systematic study of the various methods currently available.
  We compare different methods to each other and additionally use mock microbial community datasets and synthetically generated reads to benchmark them.

>>>>

  Studies have shown the importance of specific microbial interactions in the healthy human microbiome \cite{Lloyd-Price2016} and others have shown how changes in these interactions can lead to dysbiosis \cite{Wang2017,Gilbert2016,Belizario2015}.
  While direct measurement of interactions is challenging, a lot of effort has gone into measuring correlations.
  Co-occurrence relationships in microbial communities may be driven by microbial interactions, although the extent and nature of their relationship is highly debated.
  Each interaction within this complex ecological network can have a positive effect, a negative effect or no effect on the species involved.
  Bacteria that compete for the same nutrient will have a negative co-occurrence relationship \cite{Ghoul2016} whereas cross-feeding between species leads to a positive co-occurrence relationship \cite{DSouza2018}.
  The microbial interaction networks are highly dynamic, and they constantly reorganize in a varying environment.
  Even under static conditions, these interactions are often difficult to predict due to their non-linear nature \cite{Konopka2015}.
  Compounding on this complexity is the fact that these interaction networks usually involve thousands of species.

@@

  The methodology for the analysis of 16S rRNA sequence data is not very straightforward and there are a myriad of tools for each step of the process, making the analysis complicated and not very reproducible.
  But because there does not exist a dataset wherein the microbial interactions have been fully characterized, there is no straightforward way to determine which set of tools or methods generate the most accurate networks.
  In this study, we propose to build a standardized 16S data-analysis pipeline that will produce robust and reproducible co-occurrence networks from community 16S sequence data.
  We do this by conducting a systematic study of the various methods currently available.
  We compare different methods to each other and additionally use mock microbial community datasets and synthetically generated reads to benchmark them.
